---
title: "data1"
author: "Mario"
date: "May 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(plotly)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(shiny)
```

Creating a map of Los Angeles in r is simple. There are many packages with map capabilities of making a map of Los Angeles. Example of map makingpakcages in r are leaftlet and ggmap. 

The data can be set to a geo location and thus give a better view of what the data is representing. For example, California can bebrokendown into counties and the data aquire from the census can be shown to represent the corresponding county. 

The same can be said LA county would be split in to its inner cities, and would give out cencus data, and other economic information. 

This would also show patterns inside LA county. For example, traffic movements, transportation access,crime comited. 

This program is also going to have interative tables.

Tasks:

* Get list of where to get data:
  + US Census
    + Get correct librarries.  get focus data on los angeles.
* get LA county map in leaflet.
* Get a list of interactive tables you may use. 
* Hook up the live data from i.e. census to interactive table. 
* Hook up the interactive map with the data. 

Useful Websites [Shows how to use tidycensus](https://www.surveillancerepository.org/analyze-us-census-data-r-tidycensus)



```{r ToGetCensesInformation, include=FALSE}
### Not running.
##
library(tidycensus) # Might need API Key.
library(censusapi) # Ke for census API: "dc0d6cdb4939712b447d2a061dee96a84316802e"
Sys.setenv(CENSUS_KEY="dc0d6cdb4939712b447d2a061dee96a84316802e") # Need to run after restarting the program.
# Sys.getenv("CENSUS_API_KEY") # Shows key saved.
```


```{r getsData, include=FALSE}

mo2ormore <- get_acs(geography = "county", state = "CA", 
              variables = "B07004G_004", geometry = TRUE) # B07004G_004 = Geographical Mobility in the Past Year (Two or More Races) for Current Residence in the United States

```


This map was created using ggplot and tidycensus. The map is maping B07004G_004 = Geographical Mobility in the Past Year (Two or More Races) for Current Residence in the United States. 


```{r echo=FALSE}
ggplot(mo2ormore, aes(fill = estimate)) + geom_sf() #This will map varibles.
```
#########################################################################################################################

